A Domain Specific Language for SpectreGuard

### 2020-12-11 paper/main.tex
wibble
Winskel; prior work on the theory of information flow

\noindent Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
to the public variable \ttt{publicArray}. The leak occurs despite the fact that the two variables have different
sensitivity annotations. This is the
result of information being indirectly leaked from the secret variable to the
public variable via a control flow construct: in this case, the innermost \ttt{for} loop.

@@

A more complicated example is \ttt{example6} in the following:

@@

@@

@@

>>>>

\noindent Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
to the public variable \ttt{publicArray}. The leak occurs despite the fact that the two variables have different
sensitivity annotations. This is the
result of information being indirectly leaked from the secret variable to the
public variable via a control flow construct: in this case, the innermost \ttt{for} loop. Such an example has been studied from programming language perspective before; for instance
in~\cite{InfoFlowAnalysis}.

@@

A more complicated example is \ttt{example5} in the following:

@@

As mentioned previously, a theory of \textit{information flow} in the context of
both computer security and programming languag theory has been developed. A description
of this theory is given in~\cite{InfoFlowAnalysis}.

@@

More broadly, a similar example of a language being represented similarly, as an
pure expression language separated from a command language, can be found in
Winskel's 1993 book in the form of the \textbf{IMP} language.\cite{WinskelBook} This
book provides an in-depth look at the three major mathematical formalizations
of programming language semantics (axiomatic semantics, operational semantics and
denotational semantics) and uses them to analyze \textbf{IMP}

@@

Other possible leak paths should also be investigated. While outside the scope of this paper,
it there could be leaks which occur under circumstances other than direct copies or the indirect
leaks described in Section~\ref{sec:Analysis}. In future work, it would be useful to either
classify more leak paths (and deal with them appropriately) or prove that, in fact, no such additional
leak paths exist (at least, within a certain threat model).

A related topic would be enriching the theoretical background of the leak analysis tool. The theory of
programming language semantics, particularly denotational semantics and operational semantics~\cite{WinskelBook}, as well
as the theory of information flow~\cite{InfoFlowAnalysis}, would be particularly applicable here.
